Visually pleasing knot projections

### 2022-06-08 inst/jma_rebuttal_review3.tex

\textcolor{blue}{I don't have a good answer to that, other than to
  point out that the focus of the manuscript was to investigate the
  visual appearance of knots using mathematical optimization routines.
  I do not wish to rule out using other G2-continuous splines, and it
  might be interesting some day to consider (e.g.) B-splines.  But as
  I say above, Bezier curves are a good starting point.}

And, if forced by the chosen tool to use Bezier curves, why not place
nodes at the crossing points, (and one or two more for large loopy
lobes between subsequent crossing points)?  -- This would allow the
user to place the crossing points far enough apart to start with, and
this would make it easy to set the Bezier handles to force right-angle
crossings.

Also, the implementation in the ``badness function" seems far from
optimal.  ``Total crossing angles()" does not address a key problem
directly: If one wants to avoid highly acute crossing angles, then
this can be addressed in a much more sensitive way with a function
such as 1/ sqr( cross.angle ).  This would go to infinity in the worst
case!  It also corresponds more directly to the way that excessive
curvature is avoided by minimizing ``bending energy," which is the
integral over the square of curvature -- or: 1/ sqr( curve-radius).
These are some ``math" issues that readers of JMA would be interested
in.

\textcolor{blue}{Function {\tt total\_crossing\_angles()} was poorly
  named.  With crossing angles $\theta_i$, $i=1,2,\ldots k$ the
  function actually returns $\sum_{i=1}^k\left(\cos\theta_i\right)^2$.
  \\ \\}

@@

\textcolor{blue}{Bosch-type symmetry refers to Bosch (2010) which was
  cited in the previous sentence.\\ \\ old text: The package
  implements Bosch-type symmetry\ldots \\ \\ new text: The package
  implements symmetry in a similar way to that of Bosch (2010)\ldots}

$>>$ If all nodes fulfill the specified symmetry constraints (as shown
on page 11, lines 15-22 and on lines 35-43), but the connection
diagram does not completely adhere to the specified symmetry - What
happens? - Does the package check this and let the user know about the
discrepancy?

Page 10 lines 56-58: ``Minimizing the badness is not entirely
straightforward..."  -- What is the problem?  I think that if all the
points are moved jointly within the specified symmetry constraints, an
optimized symmetrical solution will result.

\textcolor{blue}{The problem is reconstructing the knot from the
  minimal set of of nodes and the various types of imposed symmetry.
  This is not difficult exactly, but not entirely straightforward
  either.\\ \\ Also, optimizing high-dimensional functions is rarely
  straightforward: the search space is large; in my field of
  computational ecology we talk of the ``curse of dimensionality''.
  One has to contend with a wide variety of frustrating issues such as
  local extrema, expensive function evaluation, and not least the
  inadequacies of Euclidean distance as a metric for the domain.
  Dimensionally cursed problems such as that addressed by {\tt knotR}
  are sometimes literally intractable.  My considered view is that
  Nelder-Mead simplex technique used in the package is unreasonably
  effective.\\ \\ }

### 2022-06-08 inst/jma_rebuttal_review3.tex

Page 10 lines 56-58: ``Minimizing the badness is not entirely
straightforward..."  -- What is the problem?  I think that if all the
points are moved jointly within the specified symmetry constraints, an
optimized symmetrical solution will result.

\textcolor{blue}{The problem is reconstructing the knot from the
  minimal set of of nodes and the various types of imposed symmetry.
  This is not difficult exactly, but not entirely straightforward
  either.\\ \\ Also, optimizing high-dimensional functions is rarely
  straightforward: the search space is large; in my field of
  computational ecology we talk of the ``curse of dimensionality''.
  One has to contend with a wide variety of frustrating issues such as
  local extrema, expensive function evaluation, and not least the
  inadequacies of Euclidean distance as a metric for the domain.
  Dimensionally cursed problems such as that addressed by {\tt knotR}
  are sometimes literally intractable.  My considered view is that
  Nelder-Mead simplex technique used in the package is unreasonably
  effective.\\ \\ }

{The above two comments suggest, that it might be advantageous to use
  some hierarchy in the representation of symmetrical knots: Only
  specify the curve for one unique fragment of the knot curve, and
  compose the complete curve by instancing that fragment with
  mirroring and rotation as required to construct the complete knot!
  The optimization would then only have to be done for this unique
  fragment (with proper end-conditions).  If this same hierarchy is
  also used in the graphical display of the knot curve, the user could
  easily make adjustments to just a few nodes, while always
  automatically obtaining the desired symmetrical result.}

\textcolor{blue}{This is exactly what I have done!  The referee gives
  an accurate summary of the code's methodology.\\ \\}

@@

RE: ``Further work might include functionality to deal
with links."  $>>$ Readers may think that this would be a trivial
extension.  Please add a paragraph like the one you wrote in response
to Reviewer 1, to explain why the extension to links may be more
difficult than one might think.

\textcolor{blue}{Done, new subsection ``some reflections on links''
  at the end, under ``conclusions and further work''}

RE: ``In the broader context of optimization in art, we observe that
numerical optimization techniques can produce aesthetically pleasing
results, an observation that might find uptake by graphic artists."
$>>$ This only holds with the proviso that we can think of a good
mathematical formulations to capture the various features that capture
aesthetics appropriately.  - This then becomes the real ``art."

\textcolor{blue}{ An insightful observation.\\ \\ OLD TEXT In the
  broader context of optimisation in art, we observe that numerical
  optimisation techniques can produce aesthetically pleasing results,
  an observation that might find uptake by graphic artists.\\ \\ NEW
  TEXT In the broader context of optimisation in art, we observe that
  numerical optimisation techniques can produce aesthetically pleasing
  results, an observation that might find uptake by graphic artists.
  Indeed, one could argue that real art lies in the capturing of
  mathematical formulations of aesthetics.  \\ \\ }

### 2022-06-09 inst/jma_rebuttal_review3.tex

RE: ``In the broader context of optimization in art, we observe that
numerical optimization techniques can produce aesthetically pleasing
results, an observation that might find uptake by graphic artists."
$>>$ This only holds with the proviso that we can think of a good
mathematical formulations to capture the various features that capture
aesthetics appropriately.  - This then becomes the real ``art."

\textcolor{blue}{ An insightful observation.\\ \\ OLD TEXT In the
  broader context of optimisation in art, we observe that numerical
  optimisation techniques can produce aesthetically pleasing results,
  an observation that might find uptake by graphic artists.\\ \\ NEW
  TEXT In the broader context of optimisation in art, we observe that
  numerical optimisation techniques can produce aesthetically pleasing
  results, an observation that might find uptake by graphic artists.
  Indeed, one could argue that real art lies in the capturing of
  mathematical formulations of aesthetics.  \\ \\ }

Gallery:

Knot diagrams $8_3$ through $8_6$ in Figure 12 stand out with their helices
too tightly wound.  The two criteria on page 4, lines 54 and 55 do not
seem to be sufficiently enforced.  I suggest adjusting these figures
in the spirit of Figure 9b.  This may happen automatically with a
better ``badness function" that penalizes non-orthogonal crossing
angles more directly.

\textcolor{blue}{The referee is correct to say that changing the
  badness function would result in figures less like 9a and more like
  9b.  But I would take issue with the phrase ``too tightly wound''.
  I have polled my colleauges who appear to be evenly split between
  preferring 9a and 9b.  The comparison appears to elicit strong
  opinions here at AUT.  Proponents of 9b point to the broader winding
  along the central helix, while those of 9a point to the more liquid
  and languid appearance, and in particular emphasise the absence of
  retrograde curvature at the bottom.  I have added a brief discussion
  of these issues to the caption of figure 12 [which is now figure 14
    of the resubmission].  I would observe that the {\tt knotR}
  package makes such discussions possible.\\ \\}

### 2022-06-09 inst/jma_knot.tex
fixes #72
fixes #73

In the broader context of optimisation in art, we observe that
numerical optimisation techniques can produce aesthetically pleasing
results, an observation that might find uptake by graphic artists.

@@

\begin{figure}[htbp]
  \begin{center}
\includegraphics[width=13cm]{knots_to_8crossings}  % created by inst/knotter.R
\caption{All \label{all8} prime knots with 8 or fewer crossings,
notation following Rolfsen~\cite{rolfsen1976}}
  \end{center}
\end{figure}

>>>>

In the broader context of optimisation in art, we observe that
numerical optimisation techniques can produce aesthetically pleasing
results, an observation that might find uptake by graphic artists.
Indeed, one could argue that real art lies in the capturing of
mathematical formulations of aesthetics.

@@

\begin{figure}[htbp]
  \begin{center}
\includegraphics[width=13cm]{knots_to_8crossings}  % created by inst/knotter.R
\caption{All \label{all8} prime knots with 8 or fewer crossings,
  notation following Rolfsen~\cite{rolfsen1976}.  Here, the penalty
  for crossing angles departing from $90^\circ$ is relatively light
  and so knot $8_3$, for example, matches the left diagram of
  Figure~\ref{figure_cca}, rather than the right}
  \end{center}
\end{figure}
